\documentclass[10pt]{article}
\usepackage[margin=0.5in]{geometry}
\usepackage{structure-style}
\pagestyle{empty}
\usepackage{amsmath}

\begin{document}

% ===== HEADER =====
\resumeHeader{Aarav Sharma}{Software Engineer}{Bhopal, India}{+91-9876543210}{aarav.sharma@email.com}{github.com/aaravsharma}{linkedin.com/in/aaravsharmaxyz}

% ===== SUMMARY =====
\section*{Professional Summary}
Results-driven Software Engineer with 4+ years of experience designing scalable distributed systems and high-performance applications. Proven expertise in backend engineering, cloud-native architectures, and data-driven optimization. Improved system efficiency by 40\% and reduced latency by 60\% across production systems.

% ===== EXPERIENCE =====
\section*{Experience}

\resumeSubheading{Senior Software Engineer}{Jan 2023 -- Present}{Google (Fictionalized Role)}{}
\resumeBullet{Designed and implemented a microservices-based architecture handling 10M+ requests, improving scalability 45\% .}
\resumeBullet{Optimized API performance by introducing Redis-based caching and database query tuning.}
\resumeBullet{Led migration from monolithic systems to Kubernetes-based container orchestration,improving release reliability.}
\resumeBullet{Built and maintained real-time data processing pipelines using distributed systems principles, enabling faster data.}

\resumeSubheading{Software Engineer}{Jul 2021 -- Dec 2022}{Amazon}{}
\resumeBullet{Developed scalable backend services using Java and Spring Boot, supporting 5M+ active users with high availability.}
\resumeBullet{Improved database performance by optimizing complex SQL queries and indexing strategies.}
\resumeBullet{Designed and implemented CI/CD pipelines using Jenkins and Docker.}
\resumeBullet{Collaborated with cross-functional teams including product managers and frontend engineers to deliver scalable features.}

\resumeSubheading{Software Engineer Intern}{Jan 2021 -- Jun 2021}{Microsoft}{}
\resumeBullet{Developed RESTful APIs using Node.js and Express, improving internal tool efficiency and enabling faster data access.}
\resumeBullet{Automated testing workflows using scripting and CI tools, reducing manual testing effort and improving code quality.}

% ===== PROJECTS =====
\section*{Projects}

\resumeProject{Real-Time Chat Application}{Backend Developer}{Node.js, WebSockets, Redis, AWS}
\resumeBullet{Designed and developed a scalable real-time chat system supporting 100K+ concurrent users using WebSockets.}
\resumeBullet{Implemented low-latency messaging pipelines, reducing message delivery time by 50\% and improving user experience.}
\resumeBullet{Deployed the application on AWS with load balancing and auto-scaling, ensuring high availability and fault tolerance.}

\resumeProject{E-commerce Recommendation System}{Machine Learning Engineer}{Python, TensorFlow, AWS}
\resumeBullet{Developed a personalized recommendation engine using collaborative filtering and deep learning.}
\resumeBullet{Processed and analyzed large-scale user interaction datasets using distributed data pipelines.}
\resumeBullet{Deployed ML models on AWS, enabling real-time inference and scalable recommendation serving for dynamic user traffic.}

\resumeProject{DevOps Automation Pipeline}{DevOps Engineer}{Docker, Kubernetes, Jenkins}
\resumeBullet{Designed and implemented a CI/CD pipeline using Jenkins, Docker, and Kubernetes, automating build.}
\resumeBullet{Reduced deployment errors by 40\% by introducing containerization and automated validation stages in the pipeline.}

% ===== SKILLS =====
\section*{Technical Skills}
\resumeItem{Languages}{Java, Python, C++, JavaScript, Go}
\resumeItem{Frameworks}{Spring Boot, React, Node.js, Django}
\resumeItem{Cloud \& DevOps}{AWS, Docker, Kubernetes, Terraform, CI/CD}
\resumeItem{Databases}{MySQL, PostgreSQL, MongoDB, Redis}
\resumeItem{Concepts}{Microservices, Distributed Systems, System Design, REST APIs}

% ===== EDUCATION =====
\section*{Education}

\resumeSubheading{M.Tech, Indian Institute of Technology}{2021 -- 2023}{CS, CGPA: 8.50/10.0} \par

\resumeSubheading{B.Tech, Indian Institute of Technology}{2017 -- 2021}{CS, CGPA: 8.70/10.0}

% ===== ACHIEVEMENTS =====
\section*{Achievements}
\resumeBullet{AWS Certified Solutions Architect Associate}
\resumeBullet{Employee of the Year Award at Amazon (2022)}
\resumeBullet{Published research paper on distributed systems optimization}
\resumeBullet{Solved 600+ problems on LeetCode (Data Structures \& Algorithms)}


\end{document}